### 2017-07-20 examples/timing_flights.Rmd
Fix typos

```{r}
benchmark(
fli_small %>%
  specify(origin ~ NULL) %>% # alt: response = day_hour
  hypothesize(null = "point", 
              p = c("EWR" = .3, "JFK" = .4, "LGA" = .3)) %>%
  generate(reps = params$rep_times, type = "simulate") %>%
  calculate(stat = "Chisq"),
replications = 1, columns = "elapsed"
)
```

@@

```{r}
benchmark(
fli_small %>%
  specify(response = half_year) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "prop", success = "f"),
replications = 1, columns = "elapsed"
)
```

>>>>

```{r}
benchmark(
fli_small %>%
  specify(origin ~ NULL) %>% # alt: response = origin
  hypothesize(null = "point", 
              p = c("EWR" = .3, "JFK" = .4, "LGA" = .3)) %>%
  generate(reps = params$rep_times, type = "simulate") %>%
  calculate(stat = "Chisq"),
replications = 1, columns = "elapsed"
)
```

@@

```{r}
benchmark(
fli_small %>%
  specify(response = half_year) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "prop", success = "h2"),
replications = 1, columns = "elapsed"
)
```
